---
title: \pkg{RProtoBuf} Quick Reference Guide

# Use letters for affiliations
author:
  - name: Dirk Eddelbuettel
    affiliation: a
  - name: Romain François
    affiliation: b
  - name: Murray Stokely
    affiliation: c

address:
  - code: a
    address: \url{http://dirk.eddelbuettel.com}
  - code: b
    address: \url{https://romain.rbind.io/}
  - code: c
    address: \url{https://stokely.org}

# For footer text
lead_author_surname: Eddelbuettel, François and Stokely

# Place DOI URL or CRAN Package URL here
doi: "https://cran.r-project.org/package=RProtoBuf"

# Customize footer, eg by referencing the vignette
footer_contents: "RProtoBuf Vignette"

# Produce a pinp document
output: pinp::pinp

header-includes: >
  \newcommand{\proglang}[1]{\textsf{#1}}
  \newcommand{\pkg}[1]{\textbf{#1}}
  \newcommand{\faq}[1]{FAQ~\ref{#1}}
  \newcommand{\rdoc}[2]{\href{http://www.rdocumentation.org/packages/#1/functions/#2}{\code{#2}}}
  \newcommand{\sugar}{\textsl{Rcpp sugar}~}

vignette: >
  %\VignetteIndexEntry{RProtoBuf-quickref}
  %\VignetteKeywords{RProtoBuf, Protocol Buffers, package}
  %\VignetteDepends{RProtoBuf}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r init, echo=FALSE}
library("RProtoBuf")
options("width"=48)
```

## Example proto file

```{r readab, echo=FALSE, comment=""}
ab.proto <- system.file("proto", "addressbook.proto", package = "RProtoBuf")
writeLines(readLines(ab.proto))
```

## Read proto description files

```{r readproto, eval=FALSE}
readProtoFiles("somefile.proto")
readProtoFiles(dir = somedir)
readProtoFiles(package = AnRPackage)
```

## Create a message

```{r createmsg}
message <- new(tutorial.Person, id = 0,
               name = "Romain Francois",
               email = "francoisromain@free.fr")
```


## Serialize a message to a file or binary connection

```{r serialize}
# to a file
tf1 <- tempfile()
message$serialize(tf1)

# to a binary connection
tf2 <- tempfile()
con <- file(tf2, open = "wb")
message$serialize(con)
close(con)

# retrieve the payload
message$serialize(NULL)
```

## Read a message from a file or binary connection}

```{r readbin, eval=FALSE}
# from a file
tutorial.Person$read(tf1)
# from a connection
con <- file(tf2, open = "rb")
tutorial.Person$read(con)
close(con)
```

## Get/Set fields

```{r getset}
email <- message$email
message$id <- 2
message[["name"]] <- "Romain"
id <- message[[2]] # tag number for 'id'
```


## Message methods

\begin{center}
\begin{small}
\begin{tabular}{cp{2.2in}}
\hline
\texttt{has} & Indicates if a message has a given field.   \\
\texttt{clone} & Creates a clone of the message \\
\texttt{isInitialized}  & Indicates if a message has all its required fields set\\
\texttt{serialize} & serialize a message to a file or a binary connection or retrieve the message payload as a raw vector\\
\texttt{clear}  & Clear one or several fields of a message, or the entire message\\
\texttt{size}  & The number of elements in a message field\\
\texttt{bytesize}  & The number of bytes the message would take once serialized\\
\hline
\texttt{swap}  & swap elements of a repeated field of a message\\
\texttt{set}  & set elements of a repeated field\\
\texttt{fetch}  & fetch elements of a repeated field\\
\texttt{add}  & add elements to a repeated field \\
\hline
\texttt{str}  & the R structure of the message\\
\texttt{as.character}  & character representation of a message\\
\texttt{toString}  & character representation of a message (same as \texttt{as.character}) \\
\texttt{update}  & updates several fields of a message at once\\
\texttt{descriptor} & get the descriptor of the message type of this message\\
\hline
\end{tabular}
\end{small}
\end{center}


## More info

\begin{center}
\begin{small}
\begin{tabular}{cp{2.2in}}
Full Vignette & \verb|vignette("RProtoBuf-intro")| \\
JSS Paper & \verb|vignette("RProtoBuf-paper")| \\
Protocol Buffers & \url{https://protobuf.dev/} \\
RProtoBuf & \url{https://github.com/eddelbuettel/rprotobuf}\\
\end{tabular}
\end{small}
\end{center}
